PANCHANGE_data_preprocessing

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd

++MD: Do we want to name the RAMP dataset something different, if the algorithm will need to be changed because they have categorical age and gender not sex? (otherwise can remove the if statement and rename the dataset 'dat.full' instead of dat.coping)
++KT: this is not the bit that needs changing for RAMP so have taken this out. 
```{r clean respiratory dataset}
respiratory <- respiratory.raw.id

dat.coping <- left_join(
  x = dat,
  y = respiratory,
  by = "ID"
)

# Probable COVID-19 case identification
Algorithm from Menni et al. to identify probable COVID-19
Variables required:
- Sex: 	0 Female, 1 Male
- Other binary variables: 0 No, 1 Yes       
- "respiratory.anosmia_binary": loss of smell or taste  
- "respiratory.pcough_binary":	Persistent cough
- "respiratory.fatigue_binary": Severe fatigue
- "respiratory.skipped_meals_binary": Skipped meals

>>>>

```{r clean respiratory dataset}
respiratory <- respiratory.raw.id

dat.coping <- left_join(
  x = dat,
  y = respiratory,
  by = "ID"
)
```

# Probable COVID-19 case identification

Algorithm from Menni et al. to identify probable COVID-19
Variables required:
- Sex: 	0 Female, 1 Male
- Other binary variables: 0 No, 1 Yes       
- "respiratory.anosmia_binary": loss of smell or taste  
- "respiratory.pcough_binary":	Persistent cough
- "respiratory.fatigue_binary": Severe fatigue
- "respiratory.skipped_meals_binary": Skipped meals
